---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# defvalues

<!-- badges: start -->
<!-- badges: end -->

The main goal of `defvalues` package is to be a tool that helps the user to
deflate values easily and quickly. The package has one main function: 
`deflate_values()`. This function wraps the `deflateBR::deflate()` function, and
adds some features based in non standard evaluation programming pattern provided
by `rlang` package. This pattern allows the user to use the function in a more
intuitive way, without the need to use the `{{ }}` operator and pass more than
one variable to deflate.

## Installation

You can install the development version of `defvalues` from [GitHub](https://github.com/) with:

``` r

# install.packages("pak")
pak::pak("fabrferreira/defvalues")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(defvalues)
## basic example code
```

